\documentclass{article}
\synctex=1
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[hidelinks,colorlinks=false]{hyperref}
\usepackage{helvet}
\usepackage[margin=0.75in]{geometry}
\usepackage{enumitem}
%\setitemize{noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt}
\setitemize{leftmargin=10pt,itemindent=10pt, noitemsep, topsep=4pt, parsep=2pt, partopsep=2pt}
\renewcommand{\familydefault}{\sfdefault}
\textheight=10in
\pagestyle{empty}
%\raggedbottom
\raggedright

%  \renewcommand{\encodingdefault}{cg}
  %\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }
% DEFINITIONS FOR RESUME
\newcommand{\area}[2]{\vspace*{-9pt} \begin{verse}\textbf{#1}   #2 \end{verse}  }
\newcommand{\lineunder}{\vspace*{-8pt} \\ \hspace*{-18pt} \hrulefill \\}
\newcommand{\header}[1]{{\hspace*{-15pt}\vspace*{6pt} \textsc{#1}} \vspace*{-6pt} \lineunder}
\newcommand{\employer}[3]{{ \textbf{#1} (#2) \underline{\textbf{\emph{#3}}}\\  }}
\newcommand{\contact}[3]{
\vspace*{-8pt}
\begin{center}
{  {#1}}\\
#2 \lineunder 
#3
\end{center}
\vspace*{-8pt}
}
\newenvironment{achievements}{\begin{list}{$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}\end{list}}
\newcommand{\schoolwithcourses}[3]{
 \textbf{#1} #2 $\bullet$ #3\\ 
\vspace*{5pt}
}
\newcommand{\school}[3]{
 \textbf{#1} #2 $\bullet$ #3\\
}
% END RESUME DEFINITIONS


%tikz
\usepackage{tikz}
\usetikzlibrary{shapes,arrows}

\begin{document}

\small
\smallskip
\vspace*{-44pt}

\contact{\href{http://jasonlarkin.org}{\LARGE{Jason M Larkin, MS, P}\lowercase{h}\LARGE{D}, Consultant}}
{\href{mailto:jasonlarkin84@gmail.com}{jasonlarkin84@gmail.com} $\bullet$ 
\href{http://jasonlarkin.org}{http://jasonlarkin.org} }

%$\bullet$ 
%\textbf{Note: }\href{https://github.com/jasonlarkin/cmu-doc/raw/master/cv/stash/jasonlarkin_cv.pdf}
%{Red are hyperlinks in digital copy}}

\header{\large{Career Overview}}

\textbf{I learn quickly and seek complex problems}. I have extensive experience in \textbf{\href{http://jasonlarkin.org/research}{research} and \href{http://jasonlarkin.org/development}{development}} in \href{http://jasonlarkin.org/diverse_fields}{diverse  fields}, collaborating in \href{http://jasonlarkin.org/multi-disciplinary}{multi-disciplinary} teams \href{http://jasonlarkin.org/globe}{globally}, delivering my research in \textbf{\href{http://jasonlarkin.org/pub.html}{publications} and \href{http://jasonlarkin.org/pres.html}{presentations}}. 

%\href{http://jasonlarkin.org}{\normalsize{\textbf{I learn quickly and seek complex problems}}}. I specialize in multi-\href{https://en.wikipedia.org/wiki/Multiscale_modeling}{scale} / \href{https://en.wikipedia.org/wiki/Multiphysics}{physics} modeling and prediction with varying levels of complexity (i.e., \href{https://en.wikipedia.org/wiki/Back-of-the-envelope_calculation}{"back of the envelope"} versus \href{https://en.wikipedia.org/wiki/Supercomputer}{computationally-intensive} \href{http://jasonlarkin.github.io/projects-phd-mfp.html}{simulation}). I have extensive experience performing \href{http://jasonlarkin.org/research}{research} and \href{http://jasonlarkin.org/development}{development} in \href{http://jasonlarkin.org/diverse_fields}{diverse fields} and have   collaborated in \href{http://jasonlarkin.org/multi-disciplinary}{multi-disciplinary} teams \href{http://jasonlarkin.org/globe}{across the globe}. I have delivered the results of my research  through \href{http://jasonlarkin.org/pub.html}{publication} and \href{http://jasonlarkin.org/pres.html}{public speaking}. \textbf{I am seeking a position to utilize and increase my knowledge of complex modeling and research.}

%The software development has covered the \href{https://www.google.com/search?q=full+stack+software&oq=full+stack+software&aqs=chrome..69i57.2623j0j7&sourceid=chrome&es_sm=122&ie=UTF-8}{"full-stack"}, was produced using \href{https://en.wikipedia.org/wiki/Agile_software_development}{Agile} methods, and has resulted in \href{http://jasonlarkin.org/research_scalable}{scalable and sustainable research}.

%https://www.youtube.com/watch?v=rjbEWeu2Nwc&feature=youtu.be#t=51m53s

%My expertise includes complex systems modeling,%
%and would like to continue...studies of complex systems...such as economic, biological,...
%and open-source collaboration to improve the way research is performed and results are disseminated.

\header{\large{Experience}}




\employer{\href{http://spiralgen.com/}{SpiralGen, Inc.}}{2013 - Present}{Senior Research Engineer}

%(2013-2015)\underline{\textbf{\emph{Software Engineer}}}

\vspace{1mm}
%\par
%My work involved research and development across the of software and hardware that supported the Spiral toolchain for , with a focus on delivering  using (see \textbf{Skills} section for more):

%My focus of expertise is identified in \textbf{bold}.
%    \item Spanned range of languages from "nearly-assembly" C to JavaScript/Python/etc.  
    \begin{itemize}

      \item \textbf{PROJECTS}

      Supported work of major commercial and research projects featuring the code-generation engine \textbf{\href{http://spiral.net/}{Spiral}}.


      \begin{itemize}
        \item \textbf{\href{http://www.darpa.mil/Our_Work/I2O/Programs/High-Assurance_Cyber_Military_Systems_(HACMS).aspx}{High-Assurance Cyber Military Systems (HACMS, \href{http://www.darpa.mil/default.aspx}{DARPA})}}

        \begin{itemize}
%\href{https://wiki.hh.se/wg211/images/e/e0/M13Franchetti.pdf}{HCOL}

          \item Automatically-optimized / \href{https://en.wikipedia.org/wiki/Formal_methods}{formally-verified} kernels for \textbf{\href{https://en.wikipedia.org/wiki/Cyber-physical_system}{Cyber-Physical Systems}} using Spiral. 

          \item Spiral plug-in for OSATE and the \textbf{Architecture Analysis $\&$ Design Language (AADL)}.

          \item \textbf{DARPA Demo Days} ground/air vehicles, virtual/physical environments.  

%\href{http://blackirobotics.com/DARPA-SN-12-26_HACMS.php}{Black-i} \href{http://www.blackirobotics.com/LandShark_UGV_UC0M.html}{Landshark}, American Built Automobile, \href{http://smaccmpilot.org/}{SMACCM Quadcopter}. 

          \item \textbf{Large/diverse} collaboration team interacting with O(1000K) Lines of Code (LOC). 
        \end{itemize}

      \item \textbf{SpiralFFT for \href{http://www.ncsa.illinois.edu}{National Center for Supercomputing  (NCSA)} \href{http://www.ncsa.illinois.edu/enabling/bluewaters}{Blue Waters}}

        \begin{itemize}

          \item Improve petascale performance of \textbf{Hybrid \href{http://en.wikipedia.org/wiki/Message_Passing_Interface}{MPI} / \href{http://en.wikipedia.org/wiki/OpenMP}{OpenMP}} \href{https://en.wikipedia.org/wiki/Fast_Fourier_transform}{FFT} and Stencils using Spiral.

          \item \textbf{\href{https://en.wikipedia.org/wiki/Pseudo-spectral_method}{Pseudo Spectral Methods}} for modeling turbulence and the \textbf{NEURON} simulation environment. 

        \end{itemize}

    \item \textbf{SpiralGen DevOps and Cloud Infrastructure}

      \begin{itemize}

        \item \textbf{\href{https://www.google.com/search?q=full+stack+software&oq=full+stack+software&aqs=chrome..69i57.2623j0j7&sourceid=chrome&es_sm=122&ie=UTF-8}{"Full-stack"}} software development for \href{https://en.wikipedia.org/wiki/Supercomputer}{high-performance}, \href{https://en.wikipedia.org/wiki/Embedded_system}{embedded}, and \href{https://en.wikipedia.org/wiki/Cloud_computing}{cloud computing}). 

        \item \textbf{\href{https://en.wikipedia.org/wiki/Agile_software_development}{Agile}} solutions in a \textbf{\href{http://en.wikipedia.org/wiki/Continuous_integration}{Continuous Integration}} using \textbf{\href{https://en.wikipedia.org/wiki/Software_configuration_management}{Software Configuration Management}} (SCM).

        \item \textbf{\href{https://dzone.com/articles/who-needs-online-ide}{WebIDE}} interface using \textbf{\href{https://en.wikipedia.org/wiki/Virtual_machine}{Virtual Machines}} (VMs) containers on \textbf{\href{https://en.wikipedia.org/wiki/Amazon_Web_Services}{Amazon Web Services}} (AWS).  

        \item Integration: \href{http://www.mathworks.com/products/matlab/}{Matlab}/\href{http://www.mathworks.com/products/simulink/}{Simulink}/\href{http://www.mathworks.com/help/matlab/ref/mex.html}{Mex}, \href{https://www.python.org/}{Python}/\href{http://cython.org/}{Cython}, \href{http://www.ros.org/}{ROS}, \href{https://www.cyberbotics.com/overview}{Webots}, \href{http://www.ls.cs.cmu.edu/KeYmaeraX/}{KeyMaeraX}, \href{http://www.wolfram.com/mathematica/}{Mathematica}.

      \end{itemize}

    \item \textbf{\href{http://www.darpa.mil/Our_Work/MTO/Programs/Power_Efficiency_Revolution_for_Embedded_Computing_Technologies_(PERFECT).aspx}{Power Efficiency Revolution for Embedded Computing Technologies (PERFECT, \href{http://www.darpa.mil/default.aspx}{DARPA})}}

      \begin{itemize}
        %\item Virtualized environment for \textbf{\href{https://en.wikipedia.org/wiki/Verilog}{Verilog}} simulations to support novel \href{http://www.contrib.andrew.cmu.edu/~bakin/publ.html}{HAMLeT} architecture.
        \item Eclipse RCP \textbf{first commerical release} of \href{http://www.spiralgen.com/new-products/spiral-fft-gpl-10}{SpiralFFT}.  
      \end{itemize}

    \item \textbf{\href{http://www.darpa.mil/program/building-resource-adaptive-software-systems}{Building Resource Adaptive Sotware Systems} (BRASS, \href{http://www.darpa.mil/default.aspx}{DARPA})}

      \begin{itemize}
        \item Test harness for Spiral-generated resource adaptive FFT for Synthetic Apeture Radar. 
      \end{itemize}

  \end{itemize}

\item \textbf{FUNDING AND RESOURCE PROPOSALS}
        \begin{itemize}
          \item \textbf{DTRA 172-003 \href{http://science.energy.gov/sbir/}{Small Business Innovation Research (SBIR)}} (PI Phase 1, in progress).

          \item \textbf{DOD 172-008 SBIR} (co-wrote Phase 1, in progress).

          \item \textbf{\href{http://science.energy.gov/sbir/}{DOE SG-13808 SBIR}} (co-wrote, \href{https://www.osti.gov/scitech/servlets/purl/1242462}{Phase 1} awarded, Phase 2 submitted).

          \item \textbf{DOD A15-102 SBIR} (PI, Phase 1 submitted).

          \item \textbf{\href{https://bluewaters.ncsa.illinois.edu/paid-ime-submissions}{NSF NCSA Blue Waters PAID IME Submission}} (Co-PI, in progress).

          \item \textbf{Spiral on \href{http://www.psc.edu/index.php/bridges}{Pittsburgh Supercomputing Bridges}} (PI, submitted). 

          \item \textbf{Optimization of 3-D FFTs for Intel Xeon Phi and NVIDIA Kepler K20 GPUs using Spiral} (PI, awarded).

        \end{itemize}


    \end{itemize}

%\end{achievements}

\employer{General Intelligence}{2013 - present}{Founder, Senior Consultant}

    \begin{itemize}

      \item \textbf{PROJECTS}
        \begin{itemize}

          \item Research and Collaboration
            \begin{itemize}

              \item \textbf{Advised on 6 projects (4 leading to publication)}: \href{http://ntpl.me.cmu.edu/publications.html}{K.D. Parrish}, \href{https://tspace.library.utoronto.ca/bitstream/1807/42871/1/Huberman_Samuel_C_201311_MASc_thesis.pdf}{S.C. Huberman}, \href{http://blogs.ubc.ca/amerimech2014/files/2014/04/ameritech_mcgaughey_apr14.pdf}{A. Jain}, \href{http://jasonlarkin.github.io/pub.html}{S. Stefanus}, \href{http://www.abi.auckland.ac.nz/people/ksam962}{N. Samaraweera}, S. Swanson

             \item \textbf{\href{https://github.com/jasonlarkin/disorder}{disorder}:} comprehensive repository of open-source code and data from PhD thesis. 

             \item \textbf{\href{https://github.com/jasonlarkin/gedit-research}{Research Analytics}}: Natural Language Processing, IBM Watson Discovery. 

 %            \item \textbf{\href{https://github.com/ntpl/ntpy}{ntpy}:} created open-source effort between \href{http://ntpl.me.cmu.edu/}{NTPL} and \href{http://www.mie.utoronto.ca/labs/atoms/}{University of Toronto}.
               

            \end{itemize}

          \item Optimizing Environment, Physical Fitness and Nutrition for Software Development
            \begin{itemize}
              \item Human Computer Interface, Optimized Nutrition/Cost, Physical Fitness and Ergonomics.
            \end{itemize}

          \item Agricultural Engineering
            \begin{itemize}
              \item Industrial Scale, Energy Optimization, Genetics.
            \end{itemize}

          \item \href{https://soundcloud.com/lintelstudio}{Music Production and Studio} 
            \begin{itemize}
              \item Virtual and Digital Audio Workstation, Theory, Performance.
            \end{itemize}
                        
          \item Data Acquistion and Signals Processing Engine
            \begin{itemize}
              \item Biological Signals processing, Event-based Pub/Sub model, Automated code generation and documentation. 
            \end{itemize}

%          \item \href{https://github.com/jasonlarkin/LapTimerLocalizations}{Performance Driving App}
%            \begin{itemize}
%              \item Pittsburgh Race Complex...
%            \end{itemize}

%\item \textbf{Research Collaborations}
%\begin{itemize}[leftmargin=10pt,itemindent=10pt, noitemsep, topsep=1pt, parsep=1pt, partopsep=1pt]
%  \item \textbf{\href{http://www.andrew.cmu.edu/user/caroling/publications.html}{Effective energy density and thermal diffusivity of Ioffe-Regel confined vibrations in amorphous silica}}: supplied \href{http://www.andrew.cmu.edu/user/caroling/}{C. S. Gorham} with source code and expertise. 

%  \item \textbf{\href{http://ntpl.me.cmu.edu/publications.html}{Origins of thermal conductivity changes in strained crystals}}: supplied \href{http://www.kdparrish.com/}{K. D. Parrish} (\href{http://www.cmu.edu/me/malen/Lab_Website/People.html}{Malen Lab}, \href{http://ntpl.me.cmu.edu/people.html}{NTPL}) with source code and expertise. 

%  \item \textbf{\href{https://tspace.library.utoronto.ca/bitstream/1807/42871/1/Huberman_Samuel_C_201311_MASc_thesis.pdf}{Phonon Properties in Superlattices}}: supplied \href{http://web.mit.edu/schuberm/www/}{Samuel Huberman} (\href{http://www.mie.utoronto.ca/labs/atoms/}{University of Toronto}, \href{http://web.mit.edu/nanoengineering/people/students.shtml}{NanoEngineering Group MIT}) with source code and expertise.  

%  \item \textbf{\href{http://jasonlarkin.github.io/pub.html}{A Search for Conformal Invariance in Compressible Two Dimensional Turbulence}}: provided \href{http://www.physicsandastronomy.pitt.edu/news-story/phd-defense-stefanus}{S. Stefanus} with  datasets and expertise.     

%  \item \textbf{\href{http://blogs.ubc.ca/amerimech2014/files/2014/04/ameritech_mcgaughey_apr14.pdf}{Phonon Transport in Periodic Materials with Feature Sizes of 1 nm to 1 $\mu$m}}: provided \href{http://ntpl.me.cmu.edu/people.html}{A. Jain} with expertise. 
%        \end{itemize}

    \end{itemize}


\employer{\href{https://www.cmu.edu/me/}{Carnegie Mellon University}}{2010-2012}{TA-Heat Transfer: lectured on conduction, convection, radiation.}
%	\begin{achievements}
%  \begin{itemize}
%    \item 
%  \end{itemize}
%	\end{achievements}

\employer{\href{http://www.engineering.pitt.edu/MEMS/}{University of Pittsburgh}}{2008}{TA-Fluid Mechanics: viscous, boundary, scale similarity, dimensional analysis.}
%  \begin{achievements}
%  \begin{itemize}
%    \item 
%  \end{itemize}
%  \end{achievements}

\employer{\href{http://www.physicsandastronomy.pitt.edu/}{University of Pittsburgh}}{2007-2009}{Lecturer-Physics: mathematics, turbulence, statistics and nonlinearity.}
%  \begin{achievements}
%  \begin{itemize}
%    \item Lectured on mathematics, bio-physics, turbulence, statistical and nonlinear phenomena. 
%  \end{itemize}
%  \end{achievements}

\employer{\href{http://www.precisiontherapeutics.com/}{Precision Therapeutics}}{2006-2007}{Intern-Technology Development: optical microscope automation design.} 
%  \begin{achievements}
%  \begin{itemize}
%    \item  
%  \end{itemize}
%  \end{achievements}

\header{\large{Education}}

\begin{itemize}[leftmargin=*]
  \item \textbf{Carnegie Mellon University} Pittsburgh, PA PhD Mechanical Engineering, 2013 GPA: 3.9/4.0
%\schoolwithcourses{Carnegie Mellon University}{Pittsburgh, PA}{PhD Mechanical Engineering, 2013 GPA: 3.85/4.00}
%\area{
  \begin{itemize}
    \item \textbf{Thesis}: \href{http://jasonlarkin.github.io/projects-phd.html}
    {Vibrational Mode Properties of Disordered Solids from High-Performance Atomistic Simulations.}
%Numerically investigated thermal properties of crystal alloys, glasses, and organic materials using classical and \href{http://en.wikipedia.org/wiki/Ab_initio_quantum_chemistry_methods}{\emph{ab initio}}-based atomistic techniques.
% Information Content: 1-10 GB
    \item \textbf{\href{http://ntpl.me.cmu.edu/research.html}{Nanostructure Thermal Conductivity}:} investigator for  
\href{http://www.wpafb.af.mil/afrl/afosr/}{AFOSR} on the \href{http://www.hpcmo.hpc.mil/cms2/index.php}{DOD's HPCMP}.
    \item \textbf{\href{https://nanochemistry.curtin.edu.au/local/docs/gulp/gulp4.2_manual.pdf}{GULP}:} \textbf{international} collaboration with \href{http://nanochemistry.curtin.edu.au/people/staff.cfm/J.Gale}{Julian Gale} at the 
\href{http://nanochemistry.curtin.edu.au/}{Nanochemistry Research Institute} at \href{http://www.curtin.edu.au/}{Curtin University}.
  \end{itemize}

  \item \textbf{University of Pittsburgh} Pittsburgh, PA MS Mechanical Engineering, 2009 GPA: 3.7/4.0
  \begin{itemize}
    \item \textbf{Thesis}: \href{http://jasonlarkin.github.io/projects-ms.html}{Statistics of Particle Concentrations in Free-Surface Turbulence.} 
    \item \textbf{\href{http://jasonlarkin.github.io/projects-ms.html}{Statistics of Free-Surface Turbulence}:} \textbf{international} collaboration with \href{http://perso.ens-lyon.fr/alain.pumir/Pumir_webpage.html}{Alain Pumir} and \href{https://groups.oist.jp/ciu/mahesh-m-bandi}{Mahesh M. Bandi}. 
%Performed experiments using novel 2D and 3D flow configurations to study turbulence as a nonlinear dynamical system. 
  \end{itemize}

  \item \textbf{University of Pittsburgh} Pittsburgh, PA BS Mechanical Engineering, 2007 GPA: 3.2/4.0
  \begin{itemize}
    \item \textbf{Research}: \href{http://en.wikipedia.org/wiki/Finite_element_method}{FEM} design of model arterial bifurcation.
  \end{itemize}

  \item \textbf{Steel Center AVTS} Jefferson Hills, PA \href{http://en.wikipedia.org/wiki/Computer-aided_design}{CADD} Certification, 2002 GPA: 3.80/4.00

\end{itemize}

\header{\Large{Skills (descending order, minimum 40 hours)}}

%\begin{achievements}

\begin{itemize}[leftmargin=*]

  \item \textbf{Publication and Public Speaking}: Journal Publication (11), Book Chapter (2), Conference Presentation (18).

  \item \textbf{Condensed Matter Physics}: quantum physics (chemistry, statistical, field), solid-state physics (molecular dynamics , nanoscale transport, statistical mechanics). \textbf{Complex Systems}: chaos and nonlinear systems (turbulence, many-body systems), complexity and information, genetics (sequencing, Markov models). \textbf{Engineering}: fluids (turbulence,  biological), continuum mechanics (solid mechanics, kinematics, elasticity), biological fluid dynamics (arterial flow, viscoelasticty), CAD AutoCAD Inventor. \textbf{Robotics} (motion planning, navigation control). \textbf{Machine Learning}: classification, natural language processing, neural networks. \textbf{Signals Processing}: (PID controller, Kalman filter, Numerical integration, sensor fusion, anomaly detection). \textbf{Coursework (50)}: statistics $\cdot$ optimization $\cdot$ numerical methods $\cdot$ molecular/electron structure $\cdot$ nanoscale transport. 

%  \item \textbf{Condensed Matter Physics, Engineering, Complex Systems}: quantum physics (chemistry, statistical, field), solid-state physics (\href{https://en.wikipedia.org/wiki/Molecular_dynamics}{molecular dynamics} , \href{http://ntpl.me.cmu.edu/}{nanoscale transport}, \href{https://en.wikipedia.org/wiki/Statistical_mechanics}{statistical mechanics}). \href{https://en.wikipedia.org/wiki/Fluid}{fluids} (turbulence,  biological), \href{https://en.wikipedia.org/wiki/Continuum_mechanics}{continuum mechanics} (\href{https://en.wikipedia.org/wiki/Solid_mechanics}{solid mechanics}, \href{https://en.wikipedia.org/wiki/Kinematics}{kinematics}, \href{https://en.wikipedia.org/wiki/Elasticity_(physics)}{elasticity}). \href{https://en.wikipedia.org/wiki/Chaos_theory}{chaotic} and \href{https://en.wikipedia.org/wiki/Nonlinear_system}{nonlinear systems} (turbulence, many-body systems), biological fluid dynamics (arterial flow, viscoelasticty) robotics (\href{https://en.wikipedia.org/wiki/Motion_planning}{motion planning}, \href{https://en.wikipedia.org/wiki/Mobile_robot_navigation}{navigation control}), genetics (\href{https://en.wikipedia.org/wiki/Markov_chain}{sequencing, Markov models}).

  \item \textbf{Full-Stack Software Engineering}: 
  \begin{itemize}
    \item \textbf{Languages (Lines of Code): } Matlab (20000), Python (10000), Perl (1000), JavaScript (4500), Java (1000), C++/C (4500), Fortran (1000). \textbf{Misc}: \LaTeX, Markdown, HTML, XML, JSON, CSS 

    \item \textbf{Software Configuration Management}: svn, git, GitHub, Jenkins, JIRA. 

\textbf{Compilers/Compilation}: GNU, Intel, Visual Studio, MinGW, Cray, Cython, Mex, Ant, make, cmake, catkin$\_$make, MSBuild, Maven. 

\textbf{Integrated Environments}: Visual Studio, Eclipse/Che, Matlab/Simulink, ROS, OSATE/AADL.

\textbf{Cloud Computing}: Amazon Web Service (AWS), Docker, VirtualBox/VMWare, nodejs, nginx, mongodb, Operating Systems: Ubuntu, Red Hat, CentOS, CoreOS, OSX, Windows (XP, 7, 8, Server).

\textbf{Documentation}: \href{http://www.doxygen.org}{Doxygen}, JSDoc, lex/flex.

%    \item \href{http://en.wikipedia.org/wiki/Software_configuration_management}{SCM} (\href{http://subversion.apache.org/}{svn}, \href{http://git-scm.com/}{git}, \href{http://jenkins-ci.org/}{Jenkins}). \textbf{Compilers/Compilation}: \href{http://gcc.gnu.org/}{GNU}, \href{https://software.intel.com/en-us/c-compilers}{Intel C/C++}, Visual Studio, \href{http://www.mingw.org/}{MinGW}, \href{http://cython.org/}{Cython}, \href{http://www.mathworks.com/help/matlab/ref/mex.html}{Mex}, \href{http://ant.apache.org/}{Ant}, \href{http://www.gnu.org/software/make/}{make}, \href{http://www.cmake.org/}{cmake}, \href{http://wiki.ros.org/catkin/commands/catkin$\_$make}{catkin$\_$make}, \href{http://en.wikipedia.org/wiki/MSBuild}{MSBuild}, \href{http://maven.apache.org/}{Maven}, \href{http://www.mathworks.com/help/matlab/ref/mex.html}{Mex}, \href{http://cython.org/}{Cython}. \textbf{Integrated Environments}: \href{http://www.visualstudio.com/}{Visual Studio}, \href{http://www.eclipse.org/}{Eclipse}, \href{http://www.eclipse.org/}{Matlab/Simulink}, \href{http://www.ros.org/}{ROS}. \textbf{Documentation}: \href{http://www.doxygen.org}{Doxygen}, JSDoc, lex/flex.


    \item \textbf{High-Performance Computing:} Linux cluster administration/computing, MPI / OpenMP, Vector Intrinsics (SSE/AVX/etc), CoArray Fortran, 


  \end{itemize}

  \item \textbf{Hardware:} optics/lasers, DI/DO AI/AO interfaces, automation, machining, circuitry,  robotics control.

%(\href{http://www.hrl.com/}{HRL}, \href{http://www.sri.com/}{SRI}, \href{http://www.cmu.edu/}{CMU}, \href{http://web.mit.edu/}{MIT}, \href{http://www.princeton.edu/}{Princeton}, \href{http://illinois.edu/}{UIUC}, \href{http://www.upenn.edu/}{UPenn}).
 
\end{itemize}


\end{itemize}
%\end{achievements}

\header{\Large{\href{http://jasonlarkin.github.io/pub.html}{Publications} (selected, 11 total)}}
%\begin{achievements}
\begin{itemize}[leftmargin=*]
\item "Origin of the Exceptionally Low Thermal Conductivity of Fullerene Derivative  PCBM Films", 
\href{http://jasonlarkin.github.io/projects-phd-pcbm.html}{(in progress).}
\item "Decorrelating a Compressible Turbulent Flow: an Experiment", \href{http://pre.aps.org/abstract/PRE/v82/i1/e016301}{Physical Review E 82, 016301 (2010).}
\end{itemize}
%\end{achievements}

\header{\Large{\href{http://jasonlarkin.org/pres.html}{Presentations} (selected, 18 total)}}
%\begin{achievements}
\begin{itemize}[leftmargin=*]
\item \href{https://bluewaters.ncsa.illinois.edu/documents/10157/5a0a0d37-95bf-460b-a7f0-cfadd15abec8}{"SpiralFFT for Blue Waters"}, \textbf{J.M. Larkin} \href{https://www.youtube.com/watch?v=rjbEWeu2Nwc&feature=youtu.be#t=51m53s}{\textbf{(speaker)}}, \href{https://bluewaters.ncsa.illinois.edu/paid-ime#SPIRAL FFT}{NCSA Symposium for Petascale 2015}.
\item "Virtual Crystal Approximation", \textbf{J.M. Larkin (speaker)}, \href{http://www.mrs.org/spring2013/}{2013 MRS Spring Meeting} San Francisco, CA.
\item "Generalized Fractal Dimensions...Turbulence", \textbf{J.M. Larkin (speaker)}, \href{http://meetings.aps.org/Meeting/MAR08/Content/1017}{2008 American Physical Society March Meeting}.

%PHONONS 2012 http://www-personal.umich.edu/~pipe/Phonons_2012_Abstract_Book.pdf
\end{itemize}
%\end{achievements}


%\header{\Large{Honors}}
%%\begin{achievements}
%\begin{itemize}[leftmargin=*]
%\item \href{http://www.asmeconferences.org/HT2012/}{2012 ASME MHNMT International Summer Heat Transfer Conference} \textbf{Top 5 Technical Paper}
%\item \href{http://www.cmu.edu/me/news/archive/2011/bennett-conference.html}{2011 Bennett Conference \textbf{Best Presentation}}
%\item \href{http://www.ices.cmu.edu/newsitem.asp?NewsID=749}{2011 ICES \textbf{Northrop-Gruman Fellow}}
%\item 2007-2009 \textbf{NSF Graduate Student Research Grant} University of Pittsburgh Department of Physics.
%\end{itemize}
%\end{achievements}

%\header{Memberships}
%%\begin{achievements}
%\begin{itemize}[leftmargin=*]
%\item American Physical Society $\cdot$ American Society of Mechanical Engineers 
%$\cdot$ Materials Research Society $\cdot$ Society of Industrial and Applied Mathematics $\cdot$ DOD High Performance Computing Modernization Program $\cdot$ NCSA Blue Waters PAID IME
%\end{itemize}
%%\end{achievements}

\end{document}
